Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
Clarified wall cuts a bit

A convolutional neural network was used for analyzing the raw waveform $\omega$ directly, without any preprocessing whatsoever, and without application of $WallCut(D)$. This avoids any destruction of information, and should be possible, in theory, for a neural network to handle. For this task, a very deep (20 layers in its shallowest configuration) 1-dimensional fully convolutional neural network was applied. The architecture was inspired by the M34-res network \cite{verydeepconvnets} for analysis of raw waveforms. L2 regularization was used to alleviate overfitting, and batch normalization was applied to the input. (Its hyperparameters were modified significantly through manual empirical testing as well as grid searches.)

@@

>>>>

A convolutional neural network was used for analyzing the raw waveform $\omega$ directly, without any preprocessing whatsoever. This avoids any destruction of information, and should be possible, in theory, for a neural network to handle. For this task, a very deep (20 layers in its shallowest configuration) 1-dimensional fully convolutional neural network was applied. The architecture was inspired by the M34-res network \cite{verydeepconvnets} for analysis of raw waveforms. L2 regularization was used to alleviate overfitting, and batch normalization was applied to the input. (Its hyperparameters were modified significantly through manual empirical testing as well as grid searches.)

@@

$WallCut(D)$ was not applied to the training set, because while the resonance in the vessel varies greatly depending on the position of the bubble, any visual differences in the bubble should not. In addition, applying it reduces the size of the training set considerably.
